---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jedrusiakr: Utilities for Statistics in Psychology

<!-- badges: start -->
[![R-CMD-check](https://github.com/jakub-jedrusiak/jedrusiakr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jakub-jedrusiak/jedrusiakr/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jakub-jedrusiak/jedrusiakr/branch/master/graph/badge.svg)](https://app.codecov.io/gh/jakub-jedrusiak/jedrusiakr?branch=master)
<!-- badges: end -->

A set of tools for quick exploration and reporting. The main part consists of functions used to calculate basic descriptive statistics and normality checks (mainly `opisz()` and `opisz_by()`). The types of descriptives reported are different for different types of measurement scales (nominal, ordinal and continous). The package also includes a set of functions for autoreporting (`raport_()`) that take a model and returns an example of analysis description in Polish (see *Example* below). For the time being, the package and its documentation are written only in Polish.

## Installation

You can install the development version of jedrusiakr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jakub-jedrusiak/jedrusiakr")
```

## Example

Summary statistics:

```{r summary-statistics}
library(jedrusiakr)
statystyki_opisowe_by(iris, "ilosciowa", Species, where(is.numeric))
```

Autoreporting in Polish:

```{r autoreporting, message=FALSE}
library(jedrusiakr)
library(dplyr)
model <- iris %>%
  filter(Species %in% c("setosa", "versicolor")) %>%
  t.test(Petal.Length ~ Species, .)
raport_t(model, "długością płatków u różnych gatunków irysów")
```
